\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-07-15 paper/paper.tex
Added EJH funding ack

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels and Tom Collins
for sharing his MATLAB implementation to evaluate musical patterns. Support provided in part by The Andrew~W.~Mellon Foundation, and NSF grant IIS-1117015.

>>>>

The authors would like to thank Matthew McVicar for helpful advice on comparing chord labels and Tom Collins
for sharing his MATLAB implementation to evaluate musical patterns. 
Support provided in part by The Andrew~W.~Mellon Foundation and the National Science Foundation, under grants IIS-0844654 and IIS-1117015.
